\begin{itemize}
\item 2015.03.13
  \begin{itemize}
  \item Correct \texttt{getRsearch} to \texttt{getRSearch}. (section
    \ref{sec:userdefined}).
  \item Add a function \texttt{PS::Abort} (section \ref{sec:initfin}).
  \end{itemize}
\item 2015.03.17
  \begin{itemize}
  \item Release version 1.0
  \end{itemize}
\item 2015.03.18
  \begin{itemize}
  \item Modify the licence related to class Particle Mesh.
  \end{itemize}
\item 2015.03.20
  \begin{itemize}
  \item Add the description of \texttt{PS::Comm::broadcast}.
  \end{itemize}
\item 2015.04.01
  \begin{itemize}
  \item Add a caution that class Particle Mesh does not work in the
    case of 1 MPI process.
  \end{itemize}
  \item 2015.10.07
  \begin{itemize}
  \item Add the description of PM method. Section
    \ref{sec:module_extended_PM}。
  \end{itemize}
\item 2015.12.01
  \begin{itemize}
  \item Add the description of Multiwalk method. Sections
    \ref{sec:example_userdefined_calcForceDispatch}、
    \ref{sec:example_userdefined_calcForceRetrieve}、
    \ref{sec:module_standard_treeforforce_calcforceallandwriteback}、
    \ref{sec:userdefined_calcForceDispatch}、
    \ref{sec:userdefined_calcForceRetrieve}。
  \end{itemize}
\item 2016.02.19
  \begin{itemize}
  \item Added descriptions for \texttt{getNeighborListOneParticle} in 
    \ref{sec:neighborlist}.

  \item In accordance with the above change, added the descriptions of 
    \texttt{PS:: MomentMonopoleScatter} and
    \texttt{PS::MomentQuadrupoleScatter} in 
    section  \ref{sec:MomentForSearchModeLong}.

  \item Added the descriptions of their wrappers,
    \texttt{MonopoleWithScatter} 
    and 
    \texttt{QuadrupoleWithScatter},
    to section  \ref{sec:module_treeforce_standard_search_mode_long}.

  \end{itemize}


  \item 2016.09.13
  \begin{itemize}
  \item Added APIs for removing or adding particles. The discription
    of them is added in \ref{sec:addAndRemoveParticle}.
  \item The discription of out-of-range access in type Vector is added
    in section \ref{sec:errormessage:vector_invalid_access}.
  \end{itemize}

    \item 2016.10.11
  \begin{itemize}
  \item The implementation of the operator ``[]'' in the Vector class
    is cahnged. Added remarks of the Vector class in section \ref{sec:datatype_vector}.
  \end{itemize}

  \item 2016.11.04
  \begin{itemize}
  \item Added APIs for IO in sections
    \ref{sec:readParticleAscii},\ref{sec:readParticleBinary},\ref{sec:writeParticleAscii},\ref{sec:writeParticleBinary}.
  \end{itemize}

    \item 2017.07.11
  \begin{itemize}
  \item Added a discription about reusing interaction list in section
    \ref{sec:treeForForceHighLevelAPI}.
  \end{itemize}

    \item 2017.09.06
  \begin{itemize}
  \item Added API for sorting FP in particle system. The discription of this API is in section
    \ref{sec:ParticleSystem:sortParticle}.
  \item Added API for obtaining a pointer of EPJ from its id. The
    discription of this API is in section
    \ref{sec:EPJ:getId},\ref{sec:getEpjFromId}.
  \end{itemize}

    \item 2017.11.08
  \begin{itemize}
  \item Release FDPS version 4.0.
  \end{itemize}

  \item 2018.01.16
    \begin{itemize}
    \item Release FDPS version 4.0b.
      \begin{itemize}
      \item Fix a bug for memory allocation.
      \item Add destructors for TreeForForce class, etc.
      \end{itemize}
    \end{itemize}

  \item 2018.01.23
    \begin{itemize}
    \item Descriptions for APIs of the serialization of particle data in exchange of particles are added in Sections \ref{sec:FP:serialize}, \ref{sec:EPJ:serialize}, \ref{sec:SPJ:serialize},          \ref{sec:particleSystem:exchangeParticle}, and \ref{sec:treeForForceHighLevelAPI} (\textcolor{red}{specification only; not yet implemented}).
    \end{itemize}

  \item 2018.05.25
    \begin{itemize}
    \item Release FDPS version 4.0c.
      \begin{itemize}
      \item MPI C++ bindings in Particle Mesh extension are eliminated.
      \end{itemize}
    \end{itemize}

  \item 2018.06.13
    \begin{itemize}
    \item Release FDPS version 4.1.
      \begin{itemize}
      \item Fix an issue when $\theta=0$ is specified (FDPS makes superparticles in some situations).
      \item Description of orthotope type is added in Section \ref{sec:datatype_orthotope}.
      \item Description of required member functions for specific cases is added in Section of Moment class.
      \end{itemize}
    \end{itemize}

  \item 2018.06.20
    \begin{itemize}
    \item Release FDPS version 4.1a.
      \begin{itemize}
      \item Fix an omission in this section.
      \end{itemize}
    \end{itemize}

  \item 2018.08.2
    \begin{itemize}
    \item A new API \texttt{getBoundaryCondition} is added.
    \item The meaning of the argument \texttt{weight} of API \texttt{collectSampleParticle} is described in detail.
    \end{itemize}

  \item 2018.12.7
    \begin{itemize}
    \item Release FDPS version 5.0a.
       \begin{itemize}
          \item Descriptions on pre-defined classes for \newline
          \texttt{PS::SEARCH\_MODE\_LONG\_SCATTER} \newline
          \texttt{PS::SEARCH\_MODE\_LONG\_SYMMETRY} \newline
          are added to the sections of Moment and SuperParticleJ classes (\S~\ref{sec:moment} and \S~\ref{sec:superparticlej}).
          \item Descriptions on member functions \texttt{readBinary} and \texttt{writeBinary} are added to the sections of FullParticle and header classes (\S~\ref{sec:fullparticle} and \S~\ref{sec:userdefined_header}). Examples of implementations of them are also added to \S~\ref{sec:example_fullparticle} and \S~\ref{sec:example_userdefined_header}.
       \end{itemize}
    \end{itemize}

  \item 2018.12.9
    \begin{itemize}
    \item Release FDPS 5.0b.
       \begin{itemize}
          \item In accurate description of API \texttt{getNeighborListOneParticle} is fixed (No changes in the source codes of FDPS except for the version information).
       \end{itemize}
    \end{itemize}

  \item 2019.1.25
    \begin{itemize}
    \item Release FDPS 5.0c.
       \begin{itemize}
          \item A bug that causes an error in function LinkCell under certain conditions is fixed.
       \end{itemize}
    \end{itemize}

  \item 2019.3.1
    \begin{itemize}
    \item Release FDPS 5.0d.
       \begin{itemize}
          \item Fixed a bug that the size of root cell of a tree becomes too large for specific boundary conditions.
          \item Fixed a bug that member variables \texttt{make\_LET\_1st}, \texttt{make\_LET\_2nd}, \newline \texttt{exchange\_LET\_1st}, and  \texttt{exchange\_LET\_2nd} of class \texttt{PS::TimeProfile} are not correctly set for some \texttt{PS::SEARCH\_MODE} in FDPS version 5.0 - 5.0c. As we changed the scopes of time measurement, each value of these member variables is not compatible with that in FDPS version 4.1 or earlier, but the sum of them is compatible.
          \item Fixed a problem that user's code stops due to segmentation fault when the memory pool used inside FDPS runs out.
          \item This version of FDPS uses a feature of C++11. \textcolor{red}{Hence, users must add an appropriate compiler option such as \texttt{-std=c++11} in \texttt{gcc} to your C++ and CUDA compilers.}
       \end{itemize}
    \end{itemize}
    
  \item 2019.3.7
    \begin{itemize}
    \item Improved the description on TreeForForLong$\langle$,,$\rangle$::MonopoleWithCutoff.
    \end{itemize}

  \item 2019.9.6
    \begin{itemize}
    \item Release FDPS 5.0f
       \begin{itemize}
          \item Fixed a problem that triggers a compile error when compiling with option \texttt{-DPARTICLE\_SIMULATOR\_TWO\_DIMENSION}.
       \end{itemize}
    \end{itemize}

  \item 2019.9.10
    \begin{itemize}
    \item Release FDPS 5.0g
       \begin{itemize}
          \item Fixed a problem that triggers a runtime error when compiling with option \texttt{-DPARTICLE\_SIMULATOR\_TWO\_DIMENSION}.
       \end{itemize}
    \end{itemize}

  \item 2020.8.16
    \begin{itemize}
    \item Release FDPS 6.0
       \begin{itemize}
          \item PIKG (\url{https://github.com/FDPS/PIKG}) included.
       \end{itemize}
    \end{itemize}
    
  \item 2020.8.18
    \begin{itemize}
    \item Release FDPS 6.0a
       \begin{itemize}
          \item The version of PIKG bundled is updated to v0.1b
       \end{itemize}
    \end{itemize}

  \item 2020.8.19
    \begin{itemize}
    \item Release FDPS 6.0b
       \begin{itemize}
          \item The implementations of the sample codes of $N$-body simulation in \path{sample/*/nbody} are improved so that they shows better performance when using kernels generated by PIKG.
       \end{itemize}
    \end{itemize}
  \item 2020.8.28
    \begin{itemize}
    \item Release FDPS 6.0b1
       \begin{itemize}
          \item The web links, described in the tutorial documents, for the initial condition files used in the sample codes are changed.
       \end{itemize}
    \end{itemize}


  \item 2020.9.02
    \begin{itemize}
    \item Release FDPS 6.0b2
       \begin{itemize}
          \item The first argument of TreeForForce::initialize/init\_tre/fdps\_init\_tree in the sample codes are fixed.
          \item With this change, the corresponding parts in the descriptions of the tutorial documents are also fixed.
       \end{itemize}
    \end{itemize}



\end{itemize}
