\subsection{General}

%プログラムの開始と終了に必要なAPIなどを記述する。

This section describes the APIs of initialization and finalization of FDPS.

\subsection{API}

\subsubsection{PS::Initialize}

%プログラムの開始を行うには以下のAPIを呼び出す必要がある。
This API must be called to initialize FDPS.

\begin{screen}
\begin{verbatim}
void PS::Initialize
              (PS::S32 & argc,
               char ** & argv,
               const PS::S64 mpool_size=100000000);
\end{verbatim}
\end{screen}

\begin{itemize}

\item {\bf arguments}

\texttt{argc}: input. Type \texttt{PS::S32} \&. The total number of arguments on the command line.

\texttt{argv}: input. Type \texttt{char **} \&. The pointer to pointer to strings on the command line.

\texttt{mpool\_size}: input. Type \texttt{const PS::S64}. The size of memory pool inside FDPS (in bytes). The default value is $10^{8}$ bytes. 

\item {\bf returned value}

void.

\item {\bf function}

  Initialize FDPS. This API must be called before other APIs of FDPS
  are called. Note, since MPI::Init is called, that inside this API
  arguments ``argc'' and ``argv'' may change.
  
  %FDPSの初期化を行う。FDPSのAPIのうち最初に呼び出さなければならない。
  %内部ではMPI::Initを呼び出すため、引数argcとargvが変っている可能性が
  %ある。

\end{itemize}

\subsubsection{PS::Finalize}

%プログラムの終了するには以下のAPIを呼び出す必要がある。

To finalize FDPS, this API must be called.

\begin{screen}
\begin{verbatim}
void PS::Finalize();
\end{verbatim}
\end{screen}

\begin{itemize}

\item {\bf arguments}

  void.

\item {\bf return value}

  void.

\item {\bf function}

Finalize FDPS.
%FDPSの終了処理を行う。

\end{itemize}

\subsubsection{PS::Abort}

\begin{screen}
\begin{verbatim}
void PS::Abort(const PS::S32 err = -1);
\end{verbatim}
\end{screen}

\begin{itemize}

\item {\bf arguments}

err: Input. Type const {\tt PS::S32}. The termination status of a
program. Default value is -1.

\item {\bf returned value}

  void.

\item {\bf function}

  Terminate the user program abnormally. The argument is the termination
  status of the program. Under MPI environment, MPI::Abort() is called,
  otherwise exit() is called.
  
  %FDPSの異常終了処理を行う。引数はプログラムの終了ステータスである。こ
  %の引数は、MPIを使用していない場合はexit関数に渡され、MPIを使用してい
  %る場合はMPIのAbort関数に渡される。

\end{itemize}

\subsubsection{PS::DisplayInfo}

\begin{screen}
\begin{verbatim}
void PS::DisplayInfo();
\end{verbatim}
\end{screen}

\begin{itemize}

\item {\bf arguments}

  void.

\item {\bf returned value}

  void.

\item {\bf function}

  Show the license and other information of FDPS.
  %FDPSのライセンス情報などを表示する。

\end{itemize}
