\subsubsection{Summary}\texttt{Header} class defines the format of header of input/output files. This class is required if users use API for file I/O provided by FDPS (\texttt{ParticleSystem::readParticleAscii},  \texttt{ParticleSystem::writeParticleAscii}, \texttt{ParticleSystem::readParticleBinary}, and \texttt{ParticleSystem::writeParticleBinary}) and want to add header information to input/output file. Below, we describe the rules for defining the member functions required from provided input/output API. There is no functions which is always required.\subsubsection{Premise}Let us take \texttt{Hdr} class as an example of \texttt{Header} as below. Users can use an arbitrary name in place of \texttt{Hdr}.\subsubsection{Required member functions for specific case}%%%%%%%%\subsubsubsection{Hdr::readAscii}
\label{sec:Hdr_readAscii}\begin{screen}\begin{verbatim}class Hdr {public:    PS::S32 readAscii(FILE *fp);};\end{verbatim}\end{screen}\begin{itemize}\item {\bf Arguments}  \texttt{fp}: Input. \texttt{FILE *} type. The file pointer of the input file.\item {\bf Returns}  \texttt{PS::S32} type. Returns the value of number of particles. Returns -1 if header does not contain the number of particle.  \item {\bf Behavior}  Read the header data from the input file.\end{itemize}
%%%%%%%%\subsubsubsection{Hdr::writeAscii}\label{sec:Hdr_writeAscii}
\begin{screen}\begin{verbatim}class Hdr {public:    void writeAscii(FILE *fp);};\end{verbatim}\end{screen}\begin{itemize}\item {\bf Arguments}  \texttt{fp}: Input. \texttt{FILE *} type. The file pointer of the output file.\item {\bf Returns}  None.  \item {\bf Behavior}  Copies the header information to the output file.    \end{itemize}

%%%%%%%%  
\subsubsubsection{Hdr::readBinary}
\label{sec:Hdr_readBinary}\begin{screen}\begin{verbatim}class Hdr {public:    PS::S32 readBinary(FILE *fp);};\end{verbatim}\end{screen}\begin{itemize}\item {\bf Arguments}  \texttt{fp}: Input. \texttt{FILE *} type. The file pointer of the input file.\item {\bf Returns}  \texttt{PS::S32} type. Returns the value of number of particles. Returns -1 if header does not contain the number of particle.  \item {\bf Behavior}  Read the header data from the input file.\end{itemize}
  
%%%%%%%%  \subsubsubsection{Hdr::writeBinary}\label{sec:Hdr_writeBinary}
\begin{screen}\begin{verbatim}class Hdr {public:    void writeBinary(FILE *fp);};\end{verbatim}\end{screen}\begin{itemize}\item {\bf Arguments}  \texttt{fp}: Input. \texttt{FILE *} type. The file pointer of the output file.\item {\bf Returns}  None.  \item {\bf Behavior}  Copies the header information to the output file.    \end{itemize}
