This document is the specification of FDPS (Framework for Developing Particle Simulator) Fortran/C interface, which supports the development of massively parallel particle simulation codes in Fortran language. This document is written by Daisuke Namekata, Masaki Iwasawa, Ataru Tanikawa, Keigo Nitadori, Takayuki Muranushi, Long Wang, Natsuki Hosono, and Junichiro Makino at RIKEN Center for Computational Science.
This document is structured as follows.

In sections \ref{chap:overview}, \ref{chap:file_str_and_ftn_if_overview}, and \ref{chap:compile_and_macro}, we present prerequisites for programing with FDPS Fortran/C interface. In section \ref{chap:overview}, we show the concept of FDPS. In section \ref{chap:file_str_and_ftn_if_overview}, we present the file configuration of FDPS and FDPS Fortran/C interface. In section \ref{chap:compile_and_macro}, we describe how to compile simulation codes with FDPS.
In sections \ref{chap:data_types}, \ref{chap:user_defined}, and \ref{chap:API_spec_list}, we present information to develop simulation codes with FDPS. In section \ref{chap:data_types}, we described data types defined in FDPS Fortran/C interface. In section \ref{chap:user_defined}, we introduce user-defined types and user-defined functions required for developing codes with FDPS Fortran/C interface. In section \ref{chap:API_spec_list}, we describe APIs used to initialize and finalize FDPS. In section 9, we present modules in FDPS and their APIs.
In sections \ref{chap:error_messages} and \ref{chap:limitation}, we present troubleshooting information. In section \ref{chap:error_messages}, we describe error messages output by both FDPS and FDPS Fortran/C interface. In section \ref{chap:limitation}, we describe the limitation of FDPS and FDPS Fortran/C interface.
Finally, we describe the change log of this document in section \ref{chap:change_log}.