\begin{itemize}
\item 2015/03/17 English version created
\item 2015/06/04 Spell-checked complete version
\item 2016/01/18 Description of GPU version added (Sec. \ref{sec:use_nvidia_gpu})
\item 2018/07/11
  \begin{itemize}
  \item Typographical error correction in Section \ref{sec:getting_started}:
    \begin{itemize}
    \item Update the information of compilers tested (using FDPS ver. 4.1a)
    \item The extension of output file of the SPH sample code is wrong
    \end{itemize}
  \item Typographical error correction in Section \ref{sec:how_to_use}:
    \begin{itemize}
    \item The section number of DomainInfo class in the specification document is wrong (Sec. \ref{subsec:how_to_use_Nbody_code})
    \item The arguments of calcForceAllAndWriteBack() in the document is not consistent with the source code (Sec. \ref{subsec:how_to_use_Nbody_code})
    \end{itemize}
  \item Typographical error in Section \ref{sec:extensions}:
    \begin{itemize}
    \item Description of the PP part is not consistent with the source code (Sec. \ref{subsec:P3M})
    \item Description of the file structure is not consistent with the sample code (Sec. \ref{subsec:TreePM})
    \item The arguments of decomposeDomainAll() in the document is not consistent with the source code (Sec. \ref{subsec:TreePM})
    \end{itemize}
  \end{itemize}
\item 2018/08/22 Description of $N$-body/SPH sample code added (Sec. \ref{sec:applications})
\item 2019/07/19 Description of $N$-body/SPH sample code updated (Sec. \ref{sec:applications})
\end{itemize} 

