\documentclass{article}
\usepackage[dvipdfmx]{graphicx}
\usepackage{fancyvrb}
\usepackage{amsmath}
\setlength{\textheight}{22cm}
\setlength{\textwidth}{17cm}
\setlength{\leftmargin}{-1 in}
\setlength{\topmargin}{0.35in}
\setlength{\topmargin}{0.1in}
\setlength{\evensidemargin}{0. in}
\setlength{\oddsidemargin}{0. in}

\newenvironment{code}
{
 \VerbatimEnvironment
 \begin{Verbatim}[frame=single]%
}
{
 \end{Verbatim}%
}

\begin{document}


\parindent 0pt
\parskip 5 pt
\title{Sunway TaihuLight Programming By examples}
\author{The Codesign Team, RIKEN AICS}
\maketitle
\thispagestyle{empty}

\begin{abstract}
  Sunway TaihuLight is the supercomputer with the largest peak performance on the Earth
  at the moment.
  We would like to understand what kind of application can be executed on TaihuLight,
  what are the theoretical limits of the performance of those applications,
  and how the actual implementations achieve closer to the theoretically-given performance limits.

  The architecture of Sunway TaihuLight is different from those of
  modern computers.  Many of modern computers have multi-level memory
  hierarchy, such as: the L1, L2, L3 cache, and the main memory. On
  the contrary, Sunway TaihuLight has only two levels of memory: the
  local directive memory (LDM) is the only memory layer above the main
  memory. The core group (CG) consists of 64 computing processor
  element (CPEs) organized in 8x8 mesh.

  These architectures pose unique challenge in the optimization on
  Sunway TaihuLight. On the other hand, they provide high performance
  if we are able to understand the architectures and use them in the
  right way.

  Therefore, we summarize the knowledge for using the Sunway TaihuLight in this document,
  by collecting the set of source codes
  for Sunway TaihuLight
  and their execution and benchmark results.


\end{abstract}

\newpage\tableofcontents\newpage

\section{Exercises} \label{sec:exercises}

\subsection{Introduction to the exercises section}


% 練習編では、Sunway TaihuLightのプログラミングに必要なプリミティブを順次取り上げ、実際に動くプログラムを作りながら動作を確認していく。
In \S \ref{sec:exercises} we practice and confirm the various programming primitives of Sunway TaihuLight
by working examples.

\input{content-exercise.tex}

\section{Practical Applications} \label{sec:practical}

\subsection{Introduction to the practical application section}

% 実践編では、Sunway TaihuLightである程度まとまったプログラムを作って
% いく。具体的には、村主の担当分野であるTemporal Blockingをかけたステ
% ンシルアプリケーションを主に作りながら、TaihuLightでどうすれば性能が
% 出るかを検証していく。

In \S \ref{sec:practical}, we create larger programs

\input{content-practical.tex}

\end{document}
