\begin{itemize}\item 今日のファイル  \begin{itemize}  \item このファイル: \$(FDPS)/sandbox/tanikawa\_box/memo/tanikawa\_memo.pdf  \item SC15メモ: \$(FDPS)/sandbox/tanikawa\_box/sc15\_memo/sc15\_memo.pdf  \end{itemize}\item fdps-supportにメールが来たときの対応 \redtext{(済)}  \begin{itemize}  \item 担当決め: 谷川  \item 自動返信はあり。  \item 解決法: 担当者はチケットのところに対応を書く。対応がOKかどうか    は牧野さん。  \item 返信先: メール作成は担当者。宛先は質問者への返信。Ccに    fdps-support。差出人はfdps-support。  \end{itemize}\item 変更履歴について \redtext{(済)}  \begin{itemize}  \item ソースコードの変更はsrcのしたのCHANGELOGへ  \end{itemize}\item リリースのバージョンについて  \begin{itemize}  \item 微修正としてver. 1.0.1  \item 微修正しましたとREADME.mdに書く。文書の変更履歴はここ、ソースの    変更履歴はここ。  \item 来週くらいにリリース  \end{itemize}\item SC15 Technical paper  \begin{itemize}  \item Title: FDPS: A Novel Framework for Developing High-Performance    Particle Simulation Codes for Distributed-Memory Systems  \item Author Information: SC15メモへ  \item Requested Areas: 第1希望 Programming Systems, 第2希望    Applications  \item Keywords (2 -- 5):     \begin{itemize}    \item Algorithm: Numerical methods, linear and nonlinear systems    \item Applications: Computational earth and atmospheric sciences    \item Applicatoins: Computational astrophysics/astronomy,      chemistry, fluid dynamics, mechanics and physics    \item Programming Systems: Parallel application frameworks    \item Programming System: Tools for parallel program development      (e.g., debuggers and integrated development environments)    \end{itemize}  \item Abstract: SC15メモへ  \item Conference Presentations: Yes  \end{itemize}\item 論文のサンプルコードまでを来週の水曜までに\end{itemize}